Extended Data

### 2022-03-29 doc/manuscript/Dow_manuscript_Nature.Rmd
tiny change

# Data Availability Statement {-#Data} 
The datasets generated and analysed during the current study are available via GitHub in the *growth_phenology* repository of the ForestGEO Ecosystems & Climate Lab @ SCBI, (https://github.com/EcoClimLab/growth_phenology) and archived in Zenodo (DOI *[TBD]*).
Master versions of the dendrometer band data are available for SCBI via GitHub in the *Dendrobands* repository of the Smithsonian Conservation Biology Institute ForestGEO plot (https://github.com/SCBI-ForestGEO/Dendrobands), which is archived in Zenodo (DOI 10.5281/zenodo.5551143), and for Harvard Forest via the Harvard Forest Data Archive (https://harvardforest1.fas.harvard.edu/exist/apps/datasets/showData.html?id=HF149). 
Weather data for SCBI were obtained from the ForestGEO Climate Data Portal v1.0 (https://github.com/forestgeo/Climate/tree/master/Climate_Data/Met_Stations/SCBI), which is archived in Zenodo (DOI: 10.5281/zenodo.3958215), and the National Center for Environmental Information (NCEI) weather station located in Front Royal, Virginia (https://www.ncdc.noaa.gov/cdo-web/datasets/GHCND/stations/GHCND:USC00443229/detail).
Weather data for Harvard Forest are available through the Harvard Forest Data Archive (https://harvardforest1.fas.harvard.edu/exist/apps/datasets/showData.html?id=HF001 AND https://harvardforest1.fas.harvard.edu/exist/apps/datasets/showData.html?id=HF000).
Climate data were obtained from CRU v.4.04 via the ForestGEO Climate Data Portal v1.0 (https://github.com/forestgeo/Climate/tree/master/Climate_Data/CRU), which is archived in Zenodo (DOI: 10.5281/zenodo.3958215).
The Standardised Precipitation-Evapotranspiration Index was obtained from the ForestGEO Climate Data Portal v1.0 (https://github.com/forestgeo/Climate/tree/master/Climate_Data/SPEI), which is archived in Zenodo (DOI: 10.5281/zenodo.3958215).
Canopy foliage phenology data were extracted from the MCD12Q2 V6 Land Cover Dynamics product (a.k.a. MODIS Global Vegetation Phenology product) via Google Earth Engine (https://developers.google.com/earth-engine/datasets/catalog/MODIS_006_MCD12Q2#description). 
In addition to being archived in this project's repository, many tree-ring data sets are archived in the International Tree-Ring Data Bank (ITRDB;https://www.ncei.noaa.gov/products/paleoclimatology/tree-ring), the DendroEcological Network (DEN; https://www.uvm.edu/femc/dendro/), or the Harvard Forest Data Archive (https://harvardforest.fas.harvard.edu/harvard-forest-data-archive), as detailed in `r chron_table`. 
Original tree cores are archived at the institutions of various members of the author team (Harvard Forest, Smithsonian Conservation Biology Institute, Indiana University, and University of Idaho) and will be made available upon reasonable request.

>>>>

# Data Availability Statement {-#Data} 
The datasets generated and analysed during the current study are available via GitHub in the *growth_phenology* repository of the ForestGEO Ecosystems & Climate Lab @ SCBI, (https://github.com/EcoClimLab/growth_phenology) and archived in Zenodo (DOI *[TBD]*).
Master versions of the dendrometer band data are available for SCBI via GitHub in the *Dendrobands* repository of the Smithsonian Conservation Biology Institute ForestGEO plot (https://github.com/SCBI-ForestGEO/Dendrobands), which is archived in Zenodo (DOI 10.5281/zenodo.5551143), and for Harvard Forest via the Harvard Forest Data Archive (https://harvardforest1.fas.harvard.edu/exist/apps/datasets/showData.html?id=HF149). 
Weather data for SCBI were obtained from the ForestGEO Climate Data Portal v1.0 (https://github.com/forestgeo/Climate/tree/master/Climate_Data/Met_Stations/SCBI), which is archived in Zenodo (DOI: 10.5281/zenodo.3958215), and the National Center for Environmental Information (NCEI) weather station located in Front Royal, Virginia (https://www.ncdc.noaa.gov/cdo-web/datasets/GHCND/stations/GHCND:USC00443229/detail).
Weather data for Harvard Forest are available through the Harvard Forest Data Archive (https://harvardforest1.fas.harvard.edu/exist/apps/datasets/showData.html?id=HF001 AND https://harvardforest1.fas.harvard.edu/exist/apps/datasets/showData.html?id=HF000).
Climate data were obtained from CRU v.4.04 via the ForestGEO Climate Data Portal v1.0 (https://github.com/forestgeo/Climate/tree/master/Climate_Data/CRU), which is archived in Zenodo (DOI: 10.5281/zenodo.3958215).
The Standardised Precipitation-Evapotranspiration Index was obtained from the ForestGEO Climate Data Portal v1.0 (https://github.com/forestgeo/Climate/tree/master/Climate_Data/SPEI), which is archived in Zenodo (DOI: 10.5281/zenodo.3958215).
Canopy foliage phenology data were extracted from the MCD12Q2 V6 Land Cover Dynamics product (a.k.a. MODIS Global Vegetation Phenology product) via Google Earth Engine (https://developers.google.com/earth-engine/datasets/catalog/MODIS_006_MCD12Q2#description). 
In addition to being archived in this project's repository, many tree-ring data sets are archived in the International Tree-Ring Data Bank (ITRDB;https://www.ncei.noaa.gov/products/paleoclimatology/tree-ring), the DendroEcological Network (DEN; https://www.uvm.edu/femc/dendro/), and/or the Harvard Forest Data Archive (https://harvardforest.fas.harvard.edu/harvard-forest-data-archive), as detailed in `r chron_table`. 
Original tree cores are archived at the institutions of various members of the author team (Harvard Forest, Smithsonian Conservation Biology Institute, Indiana University, and University of Idaho) and will be made available upon reasonable request.
